---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# SGGP

[![Travis-CI Build Status](https://travis-ci.org/CollinErickson/SGGP.svg?branch=master)](https://travis-ci.org/CollinErickson/SGGP)
[![Coverage Status](https://img.shields.io/codecov/c/github/CollinErickson/SGGP/master.svg)](https://codecov.io/github/CollinErickson/SGGP?branch=master)


The goal of SGGP is to provide a sequential design of experiment algorithm that can efficiently use many points and interpolate exactly.

## Installation

You can install SGGP from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("CollinErickson/SGGP")
```

## Example

To create a SGGP object:

```{r example}
## basic example code
library(SGGP)
d <- 8
SG <- SGGPcreate(d=d,201)
print(SG)
```

A new `SGGP` object has design points that should be evaluated next, either from `SG$design` or `SG$design_unevaluated`.

```{r}
f <- function(x) {x[1]^2 + (0.5-x[2])^3 + sin(x[3])}
Y <- apply(SG$design, 1, f)
```

Once you have evaluated the design points, you can fit the object with `SGGPfit`.

```{r}
SG <- SGGPfit(SG, Y)
SG
```

