---
title: "redTime HandlingSuppData option comparison"
author: "Collin Erickson"
date: "February 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=13)
knitr::opts_chunk$set(fig.height=9)
library(ggplot2)
library(magrittr)
```

# Rerunning redTime on already gathered data with supplementary data

I took a sequence of SGGP objects from an already completed redTime run.
I gave it supplementary data and had it refit, then checked on test set.
So the points chosen had nothing to do with supp data, but we should see
that it gets better with more data.
And we can compare it to other models.

## Output dimension 10

```{r}
# s10 <- readRDS("./scratch/redTime/redTimeSuppExp2/redTimeSuppExp2_od10_object.rds")
s10 <- readRDS("../redTimeSuppExp2/redTimeSuppExp2_od10_object.rds")
s10$completed_runs %>% table
```

```{r}
df10 <- s10$outcleandf
```

```{r}
ggplot(data=df10, mapping=aes(Ngrid, RMSE, color=as.factor(Nsupp))) + geom_point(size=4) + facet_grid(. ~ package+Supp, scales="free_y") + scale_y_log10()
```


```{r}
ggplot(data=df10, mapping=aes(Ngrid, score, color=as.factor(Nsupp))) + geom_point(size=4) + facet_grid(. ~ package+Supp, scales="free_y")# + scale_y_log10()
```


```{r}
ggplot(data=df10, mapping=aes(Ngrid, CRPscore, color=as.factor(Nsupp))) + geom_point(size=4) + facet_grid(. ~ package+Supp, scales="free_y") + scale_y_log10()
```


```{r}
rm(df10)
```


## Output dimension 50

```{r}

# s50 <- readRDS("./scratch/redTime/redTimeSuppExp2/redTimeSuppExp2_od50_object.rds")
s50 <- readRDS("../redTimeSuppExp2/redTimeSuppExp2_od50_object.rds")
s50$completed_runs %>% table
```


```{r}
df50 <- s50$outcleandf
```

```{r}
ggplot(data=df50, mapping=aes(Ngrid, RMSE, color=as.factor(Nsupp))) + geom_point(size=4) + facet_grid(. ~ package+Supp, scales="free_y") + scale_y_log10()
```


```{r}
ggplot(data=df50, mapping=aes(Ngrid, score, color=as.factor(Nsupp))) + geom_point(size=4) + facet_grid(. ~ package+Supp, scales="free_y")# + scale_y_log10()
```


```{r}
ggplot(data=df50, mapping=aes(Ngrid, CRPscore, color=as.factor(Nsupp))) + geom_point(size=4) + facet_grid(. ~ package+Supp, scales="free_y") + scale_y_log10()
```


```{r}
rm(df50)
```