---
title: "Internal comparison experiment"
author: "Collin Erickson"
date: "January 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(ggplot2)
```

We are going to run an experiment using our `SGGP` code to see how the
various options affect the prediction ability of the model.

Internal options

* Selection method in append: UCB, TS, Greedy

* Correlation function: Cauchy, CauchySQ, CauchySQT, Gaussian, Power exponential, Matern 3/2, Matern 5/2

* Sampling method in fit: Laplace approx, MCMC

* Grid size: fast (1 2 4 4 4 6 8 32), slow (1 2 2 2 4 4 4 4 4 6 32)

* Batch size

* Prediction: use MAP, full Bayesian using samples

* Append blocks using RIMSE or RIMSE/point

* Point location

## Internal options for our experiment

* (3) Selection method: UCB, TS, Greedy

* (3) Corr func: CauchySQT, Gaussian, Power exp

* (2) Sampling method: Laplace, MCMC

* (2) Grid size: fast (1 2 4 4 4 6 8 32), slow (1 2 2 2 4 4 4 4 4 6 32)

* (2) Batch size: 64 or 256 up to 1024, then 512 for both

* (2) Prediction: MAP, full Bayesian

* (2) Append using RIMSE, RIMSE/point

This is $2^5 3^2 = 288$ options. We can do a fractional factorial experiment to save time.

## First experiment (Comparer2)

I saw that MCMC and full Bayesian prediction were far slower than
their alternatives.
I ran a smaller experiment on my computer with the following



* (3) Selection method: UCB, TS, Greedy

* (7) Corr func: CauchySQT, CauchySQ, Cauchy, Gaussian,
Power exp, Matern 3/2, and Matern 5/2

* (1) Sampling method: Laplace, ~~MCMC~~

* (2) Grid size: fast (1 2 4 4 4 6 8 32), slow (1 2 2 2 4 4 4 4 4 6 32)

* (2) Batch size: 64 or 256 up to 1024, then 512 for both

* (1) Prediction: MAP, ~~full Bayesian~~

* (2) Append using RIMSE, RIMSE/point

This took over a day on my laptop using 3 cores.

```{r}
e2 <- readRDS("ComparerRun2_completed.rds")
```
```{r}
e2$completed_runs %>% table
```

I look at the results and saw something weird going on.
It turns out that some of the runs became awful after large
number of points.

```{r}
stripchart(RMSE ~ nallotted, e2$outcleandf)
stripchart(RMSE ~ nallotted + corr, e2$outcleandf, las=1)

```

```{r}
ggplot(data=e2$outcleandf, mapping=aes(x=nallotted,y=RMSE, shape=factor(batchsize), color=sel.method)) + geom_point() +
  facet_grid(corr ~ .) + ggplot2::scale_y_log10()

```
```{r}
ggplot(data=e2$outcleandf, mapping=aes(x=nallotted,y=score, shape=factor(batchsize), color=sel.method)) + geom_point() +
  facet_grid(corr ~ .)
```
```{r}
ggplot(data=e2$outcleandf[e2$outcleandf$nallotted!=16384,], mapping=aes(x=nallotted,y=score, shape=factor(batchsize), color=sel.method)) + geom_point() +
  facet_grid(corr ~ .)

```


